Measuring Perceptions and Preferences for Meritocracy

### 2021-08-19 paper.Rmd
colors
- caption y color en plot

```{r merit-model, echo=FALSE, fig.cap = "Model of perception and preferences for meritocracy and non-meritocracy", fig.align='center'}
knitr::include_graphics("input/images/generalf.png")
```
The columns "Perceptions" and "Preferences" represent the distinction between these two concepts, usually confused under the label "beliefs" [@castillo_meritocracia_2019]. Perceptions refer to the extent to which people observe that meritocracy functions or applies in their society, which relates to items such as "I think hard work is important to get ahead in society". Preferences refer to normative expectations that are usually linked to a "should" expression (e.g. whether hard work should be related to payment). The rows in Figure 1 consider the distinction between meritocratic and non-meritocratic dimensions [@reynolds_perceptions_2014]. These aspects have usually been treated as different ends of the same continuum in previous research, an assumption that requires empirical scrutiny. Non-meritocratic elements usually refer to the use of personal contacts or family advantages to get ahead in life.

@@

```{r plotlikert, echo=FALSE, fig.align='center', fig.cap="Distribution of responses in the Merit Scale items", fig.height=8, fig.width=11}
#Final plot
cowplot::add_sub(
  cowplot::plot_grid(p1,p2,leg, #plot 1,2 and legend (bottom)
    align = "hv",
    axis = "a",
    nrow = 3, #2 plots
    ncol = 1, #1 column
    rel_heights = c(1,1,0.25) #fig size within plot
    ),
  label = paste0("n=",dim(dat_likert_s2)[1]
    ),        # Caption: source and sample size 
  size = 12,  # Caption font size
  hjust = -8# Caption align 
  ) %>% 
  cowplot::ggdraw() 
```

>>>>

```{r merit-model, echo=FALSE, fig.cap = "Model of perception and preferences for meritocracy and non-meritocracy", fig.align='center'}
knitr::include_graphics("input/images/generalf.png")
```
The columns "Perceptions" and "Preferences" represent the distinction between these two concepts, usually confused under the label "beliefs" [@castillo_meritocracia_2019]. Perceptions refer to the extent to which people observe that meritocracy functions or applies in their society, which relates to items such as "I think hard work is important to get ahead in society". Preferences refer to normative expectations that are usually linked to a "should" expression (e.g. whether hard work should be related to payment). The rows in Figure \@ref(fig:merit-model) consider the distinction between meritocratic and non-meritocratic dimensions [@reynolds_perceptions_2014]. These aspects have usually been treated as different ends of the same continuum in previous research, an assumption that requires empirical scrutiny. Non-meritocratic elements usually refer to the use of personal contacts or family advantages to get ahead in life.

@@

```{r plotlikert, echo=FALSE, fig.align='center', fig.cap="Distribution of responses in the Merit Scale items", fig.height=8, fig.width=11}
#Final plot
cowplot::add_sub(
  cowplot::plot_grid(p1,p2,leg, #plot 1,2 and legend (bottom)
    align = "hv",
    axis = "a",
    nrow = 3, #2 plots
    ncol = 1, #1 column
    rel_heights = c(1,1,0.25) #fig size within plot
    ),
  label = paste0("Source: Authors calculations based on Study 1 sample"," (n=",dim(na.omit(dat_likert_s2))[1],")"
    ),        # Caption: source and sample size 
  size = 12,  # Caption font size
  hjust = -0.15# Caption align 
  ) %>% 
  cowplot::ggdraw() 
```
